---
title: "Yearly Sun Spot Numbers"
author: "Omyung Richard Kwon"
date: "July 28, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Yearly Sun Spot Numbers

This Shiny web application contains a simple plot of yearly sun spot numbers from dataset **sunspot.year**.

This dataset contains the yearly sun spot numbers from 1700 to 1988 (rounded to one digit).

The application is located at below location:
<https://rkwon.shinyapps.io/YearlySunSpot/>

## sunspot.year Data Set

```{r echo=TRUE}
str(sunspot.year)

summary(sunspot.year)

```

## Sun Spot Plot

Key Capabilities:  

- A time series line plot of number of sun spots (y-axis) vs. years (x-axis)  
- Slide two buttons to select the MIN and MAX years for the Plot  
- Select/Deselect the **Show/Hide Regression Line** to show the appropriate linear regression line for the selected years  

## Sun Spot Plot

```{r pressure}
plot(time(sunspot.year), sunspot.year, type="l", xlab="Year",
     ylab="Number of Sun Spots")

abline(lm(sunspot.year~time(sunspot.year)), col="red", lwd=2)
```

